Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2021-06-14 02_Paper/paper.tex
update caption table 3.

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and 
                Decision Tree classification on our anomaly detection task. 
                The first row shows the performance of naively predicting a broken piece
                every time.}
       \label{tab:class_comp}
\end{table}

@@

Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples
quality measurements indicated a problem. This set the 
baseline over the entire data set, which would be obtained by simply labeling all samples
as faulty. For the test set, we required to classify more than 64\% of the data correctly.
Therefore, we expected any naive classifier to produce at least 64\% accuracy, which we had to surpass. In Table~\ref{tab:class_comp}, we observe that this was indeed the case for all three approaches evaluated here.

>>>>

\begin{table}
       \centering
       \begin{tabular}{ c c } \toprule
              Approach         & accuracy \\ \midrule
              Na\"ive-Baseline & 64 \% \\
              Support Vector Machine & 82 \% \\
              Multilayer Perceptron & 88 \% \\
              Decision Tree         & 98 \% \\ \bottomrule
       \end{tabular}
       \caption{Comparison of Support Vector Machine (SVM), Multilayer Perceptron and Decision Tree classification on our anomaly detection task. }
       \label{tab:class_comp}
\end{table}

@@

Results are shown in table~\ref{tab:class_comp}. For 32 of the total 50 test samples quality measurements indicated a problem. 
The first row shows the performance of naively predicting a broken piece every time. This accuracy sets the baseline over the entire data set, which would be obtained by simply labeling all samples as faulty. Therefore, we expected any naive classifier to produce at least 64\% accuracy, which we had to surpass. In Table~\ref{tab:class_comp}, we observe that this was indeed the case for all three approaches evaluated here.
